The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-08 paper/ms.tex
venn diagram and conclusions

% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\kepler}{\emph{Kepler}\xspace}
\newcommand{\hipparcos}{\emph{Hipparcos}\xspace}
\newcommand{\gaia}{\emph{Gaia}\xspace}

@@

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded. The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored. In the K2 mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and measure solar-like oscillations in 34~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~objects, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing. Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. \textcolor{red}{Aside from the restriction on stars falling on the edge of a chip}, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.

@@

@@

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

@@

>>>>

% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\kepler}{\emph{Kepler}\xspace}
\newcommand{\ktwo}{\emph{K2}\xspace}
\newcommand{\hipparcos}{\emph{Hipparcos}\xspace}
\newcommand{\gaia}{\emph{Gaia}\xspace}

@@

Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded. The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored. In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}. Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and measure solar-like oscillations in 34~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~objects, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing. Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. A Venn diagram of the sample, noting the availablilty of asteroseismic fits Section~\ref{asteroseismology} and spectroscopy (Section~\ref{spectroscopy}) is displayed in Figure~\ref{venn}. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. \textcolor{red}{Aside from the restriction on stars falling on the edge of a chip}, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.

@@

\begin{figure}
\noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
\caption{\label{venn}
Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
\end{figure}
\newpage % hack because the venn diagram doesn't work

@@

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. The other example is the B3e star HD~183362 at $G = -2.576$. A detailed study of these stars will be presented by Antoci et al., in prep.

@@

The \kepler Smear Campaign establishes a legacy sample of~102 very bright stars, with \kepler light curves that in almost all cases reveal astrophysically interesting variability. The virtue of these bright stars is that they can be studied with interferometry, and more easily with spectroscopy than fainter targets, permitting especially detailed characterization. We have therefore obtained detailed abundances of a subset of the red giants in this sample, particularly with a view to determining their provenance in the Galactic thick and thin disk populations. The science that can be done both with this sample and with this method are, however, considerably broader: while we have not attempted it in this paper, a compelling next step is to use interferometric diameter measurements and to further constrain the red giant parameters, and compare these to the constraints from \gaia. Any tension between these measurements will help test and refine the asteroseismic scaling relations, and better models will propagate through to smaller systematic uncertainties in large samples of stars too faint for interferometry. Further improvements will be revealed by the detailed modelling of individual oscillation frequencies in these giants to infer interior structure such as convective overshoot, which is at the time of writing an active topic of research. For the lower-frequency M~giants classed as LPVs in this paper, extending the systematics correction and quarter-stitching algorithms to more robustly correct their light curves without removing real signal will allow similar asteroseismic analysis, for a sample of stars that are much less well understood than their higher-frequency counterparts.

The \kepler Smear Campaign has another natural extension: while many saturated stars in \ktwo have now been observed with `halo' apertures including their unsaturated pixels, many were not, either because they were fainter than the typical $Kp \lesssim 6.5$ limit, or because in Campaigns~0-3 and~5 no such apertures were selected. There is therefore the potential for a \ktwo Smear Campaign to complete the \ktwo sample down to fainter magnitudes, complementing the very brightest stars studied with halo photometry.
